---
title: "Simple Document"
author: "Weijia Xiong"
date: 2019-09-12
output: github_document
---

I'm an R Markdown document! 

# Section 1

Here's a **code chunk** that samples from 
a _normal distribution_:

```{r echo=FALSE}
library(tidyverse)
samp = rnorm(100)
length(samp)
```

# Section 2

I can take the mean of the sample, too!
The mean is `r mean(samp)`.

```{r generate_df, echo = FALSE}
mean(samp)

plot_df = tibble(
  x = rnorm(100),
  y = 1 + 2 * x + rnorm(100)
)
```
the number of rows in `plot_df` is `r nrow(plot_df)`


```{r learning assessment 1, echo=FALSE}
library(tidyverse)
norm_df = tibble(
  norm_data = rnorm(500,mean = 1),
  norm_data_log = norm_data > 0 ,
  norm_data_abs = abs(norm_data)
)

norm_hist = hist(pull(norm_df,norm_data_abs))
ggplot(norm_df, aes(x = norm_data_abs)) + geom_histogram()
norm_median = median(pull(norm_df,norm_data))
```

The median of the variable containing absolute values is 
`r round(norm_median, digits = 2)`.



Text formatting 
------------------------------------------------------------

*italic*  or  _italic_
**bold**  or  __bold__
`code`
superscript^2^ and subscript~2~


Headings
------------------------------------------------------------

# 1st Level Header

## 2nd Level Header

### 3rd Level Header


Lists
------------------------------------------------------------

*   Bulleted list item 1

*   Item 2

    * Item 2a

    * Item 2b

1.  Numbered list item 1

1.  Item 2. The numbers are incremented automatically in the output.


Tables 
------------------------------------------------------------

First Header  | Second Header
------------- | -------------
Content Cell  | Content Cell
Content Cell  | Content Cell



* The mean of the sample is `r mean(pull(norm_df,norm_data)) `.
* The median of the sample is is `r  median(pull(norm_df,norm_data)) `.
* The standard deviation of the sample is is `r sd(pull(norm_df,norm_data)) `.


